\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-07-08 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
new cover page with more logos for the users manual

\author{$\copyright$ Princeton University (USA) and\\
 CNRS / INRIA / University of Pau (France)\\
 Version 2.1}

@@

>>>>

\author{$\copyright$ Princeton University (USA),\\
CNRS and University of Marseille (France),\\
and ETH Z\"urich (Switzerland)\\
Version 2.1}

@@

\section*{Current and past main participants or main sponsors}

\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=0.125\textwidth]{figures/logo_cnrs}\vspace*{2truemm}
\includegraphics[width=0.125\textwidth]{figures/logo_princeton}\vspace*{2truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_aix_marseille_universite}\vspace*{2truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_ETH}\vspace*{2truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_inria}\vspace*{2truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_UPPA}
\par\end{centering}

\noindent \begin{centering}
\includegraphics[width=0.15\textwidth]{figures/logo_NVIDIA}\vspace*{2truemm}
\includegraphics[width=0.125\textwidth]{figures/logo_IUF}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_Univ_Toulouse}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Caltech}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Harvard}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_IPGP}
\par\end{centering}
\end{figure}
